FastSRM: A fast, memory efficient and identifiable implementation of the shared response model

### 2022-01-04 paper/main.tex
correct abstract

\begin{abstract}
  The shared response model (SRM) provides a simple but effective framework to analyse
  fMRI data of subjects exposed to naturalistic stimuli.
  %
  However when the number
  of subjects or runs is large,
  % \bt{True, but we the experiments don't make it so explicit ?}
  fitting the model requires a large amount of memory
and computational power, which limits its use in practice.
%
Furthermore, SRM is
not identifiable, which makes the shared response difficult to interpret.

>>>>

\begin{abstract}
  The shared response model (SRM) provides a simple but effective framework to analyze
  fMRI data of subjects exposed to naturalistic stimuli.
  %
  However when the number
  of subjects or runs is large,
  % \bt{True, but we the experiments don't make it so explicit ?}
  fitting the model requires a large amount of memory
and computational power, which limits its use in practice.
%
Furthermore, SRM is
not identifiable, which makes the shared response difficult to interpret.
